%-------------------------
% Resume in LaTeX
% Author: Noel Sason
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx} % Professional Times font
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{fontawesome5}

% ---------- COLORS ----------
\definecolor{headerblue}{RGB}{26, 54, 93}
\definecolor{linkblue}{RGB}{15, 82, 186}
\definecolor{rulecolor}{RGB}{100, 100, 100}

% ---------- PAGE SETUP ----------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}

% ---------- SECTION FORMATTING ----------
\titleformat{\section}{
  \vspace{-12pt}\color{headerblue}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{rulecolor}\titlerule\vspace{-6pt}]

% ---------- CUSTOM COMMANDS ----------
\newcommand{\resumeSubheading}[4]{
  \begin{tabular*}{\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} --- \textit{#2} & \small #3 \\
    \ifx&#4&\else \multicolumn{2}{l}{\small #4} \\ \fi
  \end{tabular*}\vspace{2pt}
}
\newcommand{\resumeSubheadingSimple}[2]{
  \begin{tabular*}{\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \small #2
  \end{tabular*}\vspace{3pt}
}

\newcommand{\resumeItem}[1]{\item\small{#1}\vspace{-2pt}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=16pt, label=\textbullet, topsep=0pt, parsep=0pt, itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}

% ---------- HYPERLINK SETUP ----------
\hypersetup{
  colorlinks=true,
  linkcolor=linkblue,
  urlcolor=linkblue,
  pdfauthor={Noel Sason},
  pdftitle={Noel Sason - Resume},
}

% ==========================================
%              DOCUMENT BEGIN
% ==========================================
\begin{document}

% ---------- HEADER ----------
\begin{center}
  {\Huge\bfseries\color{headerblue} Noel Sason} \\[6pt]
  \small
  \faIcon{envelope}\;\href{mailto:noel_sason@berkeley.edu}{noel\_sason@berkeley.edu} \quad
  \faIcon{phone}\;(661) 523-9570 \quad
  \faIcon{map-marker-alt}\;Berkeley, CA \quad
  \faIcon{github}\;\href{https://github.com/noelsason}{GitHub}
\end{center}

\vspace{-15pt}

% ---------- EDUCATION ----------
\section{Education}
\resumeSubheading
  {University of California, Berkeley}
  {B.A. Molecular Biology \textbar\ B.S. Data Science}
  {Aug 2024 -- May 2028}
  {GPA: 3.82 / 4.00 \textbar\ \textbf{Relevant Coursework:} CS61B (Data Structures \& Algorithms), Data C88C (Computational Structures in Data Science)}

\vspace{-2pt}

% ---------- EXPERIENCE ----------
\section{Experience}

\resumeSubheading
  {Research Affiliate}{Lawrence Berkeley National Laboratory}{Jan 2026 -- Present}{}
\resumeItemListStart
  \resumeItem{Built Python data pipelines to transform microbial trait data from KG-Microbe, GTDB, NCBI, and study outputs into standardized wide and long TSV tables for downstream search and comparative analysis.}
  \resumeItem{Implemented aggregation, normalization, and validation logic for heterogeneous bioinformatics datasets, including feature summarization, cross-database table merging, row/trait reshaping, and automated tests to ensure analysis-ready outputs.}
\resumeItemListEnd

\resumeSubheading
  {Finance Director}{ASUC Berkeley, South Asian Ad Hoc Office}{Aug 2025 -- Present}{}
\resumeItemListStart
  \resumeItem{Direct an annual budget for a university-mandated student government body, overseeing fund allocation, internal expense tracking, and large-scale vendor payments.}
  \resumeItem{Oversee contingency funding and Wellness Fee submissions, maintaining strict compliance across  89+ tracked deadlines and university financial governance requirements.}
\resumeItemListEnd

\resumeSubheading
  {Finance Director}{South Indian Society, UC Berkeley}{Sept 2024 -- Present}{}
\resumeItemListStart
  \resumeItem{Manage end-to-end budgeting and reimbursements for a 100+ member organization; redesigned financial tracking systems, reduced reimbursement processing latency.}
  \resumeItem{Standardized financial record-keeping with automated audit trails, improving transparency and enabling data-driven spending forecasts for upcoming fiscal cycles.}
\resumeItemListEnd

% ---------- PROJECTS ----------
\section{Projects}
\resumeSubheadingSimple
  {Canvascope  --- \small\href{https://canvascope.org}{canvascope.org}}{Founder / CEO}
\resumeItemListStart
  \resumeItem{Founded a privacy-first Chrome extension platform for Canvas and Brightspace LMS indexing and semantic search, scaling to 10+ university domains with local-first processing and sub-100ms fuzzy matching.}
  \resumeItem{Built an integrated ecosystem with automated document categorization and LLM embeddings for intelligent retrieval, serving as the central hub for Lectra (See Above) and other productivity sub-products (Like MedMatch).}
  \resumeItem{Manage product strategy: authored roadmap documentation, defined role structures, and overseen Vercel deployments for a unified, cross-platform student productivity suite.}
\resumeItemListEnd

\resumeSubheadingSimple
  {Lectra --- \small\href{https://canvascope.org}{canvascope.org}}{Swift, SwiftUI, iOS Development}
\resumeItemListStart
  \resumeItem{Developed a native iOS application for Apple Pencil annotation, featuring a custom DropBridge v2 file transfer protocol for seamless document sharing with the Canvascope ecosystem.}
  \resumeItem{Implemented real-time backend synchronization using Supabase, enabling cross-platform access to annotated PDFs and intelligent categorization of handwritten notes.}
  \resumeItem{Optimized PDF rendering and stroke capture for low-latency feedback on iPad Pro displays, providing a paper-like experience for clinical and academic note-taking.}
\resumeItemListEnd
\resumeSubheadingSimple
  {RxBrief --- \small\href{https://www.rxbrief.org/}{rxbrief.org}}{Next.js, Javascript, Supabase}
\resumeItemListStart
  \resumeItem{Built a full-stack health platform featuring a live FDA drug label lookup API and real-time Supabase chat for patient-provider communication simulations.}
  \resumeItem{Developed a multi-source healthcare jobs aggregator leveraging Greenhouse, Lever, and RSS APIs; implemented server-side filtering for rapid, domain-specific search results.}
  \resumeItem{Worked with industry professionals to design and program a website tailored to what healthcare professionals need.}
\resumeItemListEnd

\resumeSubheadingSimple
  {MedMatch --- \small\href{https://medmatch.canvascope.org/}{medmatch.canvascope.org}}{Next.js, Supabase, Javascript}
\resumeItemListStart
  \resumeItem{Engineered a sophisticated matching engine that evaluates medical school eligibility across 159 institutions by comparing user coursework against 1,162 AAMC requirements.}
  \resumeItem{Built a custom PDF ETL pipeline to ingest and normalize the 2026 MSAR dataset; implemented credit-hour conversion logic and school-specific policy evaluation (e.g., AP/IB credit pooling).}
  \resumeItem{Integrated with Canvascope environment (See Above) to pull courses from current Canvas courses student is enrolled in.}
\resumeItemListEnd




% Double checking for any remaining ClearLedger items - none found.

% ---------- TECHNICAL SKILLS & CERTIFICATIONS ----------
\section{Technical Skills \& Certifications}

\vspace{-2pt}
\small
\begin{tabular*}{\textwidth}{@{}l@{\hskip 12pt}l@{}}
  \textbf{Languages \& Tools:} & Python, Java, SQL, JavaScript, HTML/CSS, Git, Swift/SwiftUI, Docker, Linux, Raspberry Pi \\
  \textbf{Data \& ML:} & Pandas, NumPy, Jupyter, Semantic Search, Embeddings (MPNet), PDF ETL, Algorithm Design \\
  \textbf{Certifications:} & \textbf{American Heart Association BLS (Basic Life Support)} \\
\end{tabular*}

\end{document}
